Metrics

### 2024-04-16 src/plots.Rmd
Add cod count for cod perf plots

    # Create label for age group
    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
    atitle <- paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")
    aref <- str_to_title(a)

@@

    # Plot boxplot
    codplot <- coddata %>%
        ggplot(aes(x = COD, y = PCCC)) +
        geom_boxplot(
            linewidth = 0.5,
            width = 0.25
        ) +
        geom_text(
            aes(label = `PCCC Min`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 1,
            position = position_nudge(y = -0.12)
        ) +
        geom_text(
            aes(label = `PCCC Max`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 0,
            position = position_nudge(y = 0.12)
        ) +
        stat_summary( # min pccc txt on boxplot
            geom = "text",
            fun = min,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = -0.06),
            size = 3
        ) +
        stat_summary( # max pccc txt on boxplot
            geom = "text",
            fun = max,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = 0.06),
            size = 3
        ) +
        labs(
            x = atitle,
            y = "PCCC (0=Low, 1=High)",
            caption = paste0("CODs removed (n<10): ", cod_low_label, ".")
        ) +
        ylim(-0.3, 1.3) +
        coord_flip() +
        theme_minimal() +
        theme(
            panel.grid = element_blank(),
            axis.line = element_blank(),
            axis.line.y = element_blank(),
            axis.title.x = element_text(margin = margin(t = 10)),
            axis.title.y = element_text(margin = margin(r = 10)),
            axis.line.x = element_line(
                color = "black",
                arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
            ),
            plot.caption = element_text(size = 6, face = "italic")
        )

>>>>

    # Create label for age group
    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
    aref <- str_to_title(a)

    # Create title for causes
    atitle <- paste0(
        "Physician Agreed ",
        alabel,
        " Records (n=", arows, ", 100%)"
    )

@@

    # Plot boxplot
    codplot <- coddata %>%
        ggplot(aes(x = COD, y = PCCC)) +
        geom_boxplot(
            linewidth = 0.5,
            width = 0.25
        ) +
        geom_text(
            aes(label = `PCCC Min`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 1,
            position = position_nudge(y = -0.12)
        ) +
        geom_text(
            aes(label = `PCCC Max`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 0,
            position = position_nudge(y = 0.12)
        ) +
        stat_summary( # min pccc txt on boxplot
            geom = "text",
            fun = min,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = -0.06),
            size = 3
        ) +
        stat_summary( # max pccc txt on boxplot
            geom = "text",
            fun = max,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = 0.06),
            size = 3
        ) +
        labs(
            x = atitle,
            y = "PCCC (0=Low, 1=High)",
            caption = if (length(cod_low_counts) > 0) paste0(
                length(causes_col) - length(cod_low_counts),
                " CODs shown / ",
                length(cod_low_counts),
                " CODs not shown (n<10): ",
                cod_low_label,
                "."
            ) else NULL
        ) +
        ylim(-0.3, 1.3) +
        coord_flip() +
        theme_minimal() +
        theme(
            panel.grid = element_blank(),
            axis.line = element_blank(),
            axis.line.y = element_blank(),
            axis.title.x = element_text(margin = margin(t = 10)),
            axis.title.y = element_text(margin = margin(r = 10)),
            axis.line.x = element_line(
                color = "black",
                arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
            ),
            plot.caption = element_text(size = 7, face = "italic")
        )
